Investigating soundscapes perception through acoustic scenes simulation

### 2018-09-04 lafaySimulatedScenePerception.tex
fixing typo

In this section, we study the scores given by the subjects while listening to the different types of scenes, namely the ideal scenes with markers, non-ideal scenes with markers, ideal scenes without markers and non-ideal scenes without markers, see Figure~\ref{fig:xp2_Ascene}. The repeated measures ANOVA applied to $\mathcal{A}_{subject}$ shows a significant effect of the environment type (Type: $F[1,10]=175$, $p<0.01$), of the presence/absence of markers (marker: $F[1,10]=7$, $p<0.05$), and of the interaction between those two factors ($F[1,10]=67$, $p<0.01$).

>>>>

In this section, we study the scores given by the subjects while listening to the different types of scenes, namely the ideal scenes with markers, non-ideal scenes with markers, ideal scenes without markers and non-ideal scenes without markers, see Figure~\ref{fig:xp2_Ascene}. The repeated measures ANOVA applied to $\mathcal{A}_{subject}$ shows a significant effect of the environment type ($F[1,10]=175$, $p<0.01$), of the presence/absence of markers ($F[1,10]=7$, $p<0.05$), and of the interaction between those two factors ($F[1,10]=67$, $p<0.01$).
